proposed ar\chapter*{ABSTRACT}
\begin{center}
  \large
  \textbf{\tatitle}
\end{center}
% Menyembunyikan nomor halaman
\thispagestyle{empty}

\begin{flushleft}
  \setlength{\tabcolsep}{0pt}
  \bfseries
  \begin{tabular}{lc@{\hspace{6pt}}l}
  Student Name / NRP&: &\name / \nrp\\
  Department&: &\engdepartment \space \engfacultyshort - ITS\\
  Advisor&: &1. \advisor\\
  & & 2. \coadvisor\\
  \end{tabular}
  \vspace{4ex}
\end{flushleft}
\textbf{Abstract}

% Isi Abstrak
Advanced autonomous mobility is limited by the latency gap between environmental perception and action execution, especially in high-precision three-dimensional (3D) object detection systems. Current state-of-the-art (SOTA) 3D detection models, despite being highly accurate, have a very high computational load and rely on non-real-time processing. This research addresses these challenges by introducing \textbf{RT-LIVO2DM}, a novel lightweight framework for simultaneous and real-time 3D odometry and object detection. By designing an architecture that synergistically integrates data from LiDAR, IMU, and visual camera sensors, \textbf{RT-LIVO2DM} is aimed at computational efficiency on resource-constrained embedded systems. Furthermore, the sensor integration presented by the \textbf{RT-LIVO2DM} framework can facilitate high-precision 3D environmental mapping. The environmental mapping data presented by \textbf{RT-LIVO2DM} paves the way for sustainable research related to Level 4/5 autonomous systems. The system's performance is quantitatively evaluated using the Waymo Open Dataset to validate its accuracy, latency, and computational load performance compared to SOTA methods. This research is expected to demonstrate the feasibility of a high-accuracy 3D perception system capable of operating within real-time constraints on autonomous platforms and provide access to the collection of information-rich driving environment data, bridging the implementation gap and paving the way for safer and more reliable Level 4/5 autonomous systems.

\vspace{2ex}
\noindent
\textbf{Kata Kunci: \emph{Real-Time, 3D Object Detection, 3D Mapping, Autonomous Mobility, Sensor Fusion, LiDAR, IMU, Computer Vision}} 